%-------------------------------------------------------------------------------
%  Experience
%-------------------------------------------------------------------------------
\cvsection{\emoji{{seedling}}:Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Assistant Programmer} % Job title
    {Upper Edge Technologies } % Organization
    {West Memphis, Ar.} % Location
    {Dec. 2019 - Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a Customer Quoting tool allow sales reps to browse the catalog while automating the manual book keeping.}
        \item {Implemented a digital RMA process with 3rd party API ( Quickbook, Bigcommerce, \& Jira ).}
        \item {Implemented new tool in PHP for interacting with 3rd party API's.}
        \item {Designed web pages for inputting parts \& laptops specs into a database.}
        \item {Built REST API's for receiving parts/laptops specs along side inventory numbers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    { Remote Teachers's Assistant } % Job title
    {Tech 901} % Organization
    {Memphis, Tn.} % Location
    {June. 2020 - Sep. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted the teacher with planning, preparation, and assessment across classroom instruction.}
        \item {Observe each student daily to assess skill, interests, and needs to facilitate meaningful instruction.}
        \item {Provided support and guidance to students through managing behavior, setting expectations and monitoring completion of assignments.}
        \item {Performed record keeping duties associated with the classroom including attendance and grade calculations.}
        \item {Assisted students with hardware or software issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
